Benchmarking the accelerated oblique random survival forest

### 2023-06-05 README.Rmd
skip the ggplot2 warnings
editing for clarity

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  dpi = 300,
  echo = FALSE,
  comment = "#>"
)

@@

In case you want a much quicker summary of the paper:

@@

- We find that the accelerated oblique RSF (`aorsf-fast` in the paper) is very fast. In fact, in a benchmark with 35 different risk prediction tasks, `aorsf-fast` was faster than all of the learners we analyzed, except for penalized Cox regression models (`glmnet-cox` in the paper). __Figure__: Distribution of time taken to fit a prediction model and compute predicted risk. The median time, in seconds, is printed and annotated for each learner by a vertical line.

@@

- We find that `aorsf-fast` has the best index of prediction accuracy out of all the learners we evaluated: __Figure__: Expected differences in index of prediction accuracy between the accelerated oblique random survival forest and other learning algorithms. A region of practical equivalence is shown by purple dotted lines, and a boundary of non-zero difference is shown by an orange dotted line at the origin.

@@

We use `targets` to coordinate the general benchmark experiment and simulation study that are presented in this research, and hope that our use of `targets` also makes it easier for others to engage with our code.

Our work can be reproduced, mostly. The only thing that can't be reproduced are the results based on datasets that we can't share with you. To replicate our work using publicly available data, you need to edit the vector of datasets passed into our `targets` pipeline (see `_targets.R`) so that it only contains publicly available data. Below is a code chunk showing which datasets you need to comment out:

@@

You'll still need to create the `nafld` data by running `nafld_build()`, which is an R function included in `R/nafld_build.R` that combines multiple datasets in the `survival` package into a dataset we analyzed in the current study.

Once you've completed these steps and installed the packages listed in `packages.R`, all you need to do is run `targets::tar_make()`. However, it will take a very long time to make the pipeline as-is and I recommend setting `run_seed` to be `1:3` (see `_targets.R` to modify this value) to request only 3 replications of Monte-Carlo cross validation be completed. Also, you are free to use only a subset of the learners by commenting out the ones you don't want to run. Here is what I'd recommend if you'd like to speed up the pipeline:

>>>>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  dpi = 300,
  warning = FALSE,
  echo = FALSE,
  comment = "#>"
)

@@

@@

- We find that the accelerated oblique RSF (`aorsf-fast` in the paper) is fast and accurate. In a benchmark with 35 different risk prediction tasks, `aorsf-fast` was faster than all of the learners we analyzed except for penalized Cox regression models (`glmnet-cox` in the paper). __Figure__: Distribution of time taken to fit a prediction model and compute predicted risk. The median time, in seconds, is printed and annotated for each learner by a vertical line.

@@

- We find that `aorsf-fast` has the best index of prediction accuracy out of all the learners we evaluated. __Figure__: Expected differences in index of prediction accuracy between the accelerated oblique random survival forest and other learning algorithms. A region of practical equivalence is shown by purple dotted lines, and a boundary of non-zero difference is shown by an orange dotted line at the origin.

@@

We use `targets` to coordinate our numerical experiments. Thus, our results on publicly available data can be reproduced by cloning our repo and running `tar_make()` with only publicly available data requested in the `targets` pipeline. Below are the steps involved:

1. Clone our repo and open the associated Rstudio project.

2. Open `packages.R` and ensure you have installed the R packages listed in this file.

3. In `_targets.R`, edit the vector of datasets passed into our `targets` pipeline so that it only contains publicly available data. Below is a code chunk showing which datasets you need to comment out to request only the publicly available ones:

@@

4. Create the `nafld` data by running `nafld_build()`, which is an R function included in `R/nafld_build.R` that combines multiple datasets in the `survival` package into a dataset we analyzed in the current study. An example of how this can be done is below:

```{r, eval=FALSE}
# load all R functions in the R directory
R.utils::sourceDirectory("R")
# load all relevant packages for this project
source("packages.R")
# run nafld_build() (takes several minutes)
nafld_build()
```

5. Run `targets::tar_make()` to make the targets pipeline, but be aware that it will take a very long time to make the pipeline as-is.

To make the process run quickly, I recommend setting `run_seed` to be `1:3` in `_targets.R` to request only 3 replications of Monte-Carlo cross validation be completed. Also in `_targets.R`, use a subset of the faster learners by commenting out the slower ones:
